The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
methods
Update manuscript.Rmd

#### Altering landcover scale

To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales. Specifically, we selected scales relevant to caribou ecology. We re-sampled landcover using the **`grainchanger` package/function[???]** (REF) at five scales: 100m, 250m, 500m, 1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017). Resampling occurred based on a modal moving window method, where XXXXX.

@@

### Metrics

Right now, we calculate mostly degree/neighborhood based metrics.

* Degree centrality
* Multidegree
* Degree deviation: standard deviation of degree across layers

>>>>

#### Altering spatial scale

To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales. Specifically, we selected scales relevant to caribou ecology. We re-sampled landcover using the **`grainchanger` package/function[???]** (REF) at five scales: 100m, 250m, 500m, 1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017). Resampling occurred based on a modal moving window method, where XXXXX. [ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]

@@

### Network metrics

We used Muxviz blah blag whatever to generate XX number of multilayer network metrics. These include four neighborhood-based metrics: degree centrality, multidegree, degree deviation, and neighbours as well as two multilayer [need better term here?] metrics: connective redundancy and relevance (see Glossary for definitions). GOING TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE)

We generated all networks 
Right now, we calculate mostly degree/neighborhood based metrics. 
* Degree centrality
* Multidegree
* Degree deviation: standard deviation of degree across layers
